MERRA-2: Carbon Analysis

### 2020-07-01 Rcode/Carbon_Analysis.Rmd
netcdf

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r}
https://goldsmr5.gesdisc.eosdis.nasa.gov/opendap/MERRA2/M2I3NVAER.5.12.4/1980/01/contents.html

url = "https://goldsmr5.gesdisc.eosdis.nasa.gov/opendap/MERRA2/M2I3NVAER.5.12.4/1980/01/MERRA2_100.inst3_3d_aer_Nv.19800101.nc4"
data = nc_open(url)

#have to delete duplicate ".nc4" in url
url2 = "https://goldsmr5.gesdisc.eosdis.nasa.gov/opendap/MERRA2/M2I3NVAER.5.12.4/2018/07/MERRA2_400.inst3_3d_aer_Nv.20180708.nc4?BCPHILIC[0:7][0:71][225:277][75:177],OCPHILIC[0:7][0:71][225:277][75:177],BCPHOBIC[0:7][0:71][225:277][75:177],OCPHOBIC[0:7][0:71][225:277][75:177],lat[225:277],time[0:7],lon[75:177],lev"
data2 = nc_open(url2)

```

```
